{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Predictions for BHBH, BHNS and NSNS binaries in LISA

### 2021-08-19 paper/tex/sections/results.tex
update variations to match noBHkick models
WR wind text and more

\todo{Remove curved line.}

@@

A further reason for the preference for low masses is that the population of BHs detectable by LISA primarily come from progenitors that formed from high metallicity gas according to our simulations (see Sec.~\ref{sec:progenitors_and_formation} also Appendix~XX). Stellar winds are stronger at high metallicity leading to increased mass loss. This affects the mass of the most massive black holes that can be formed \citep{Belczynski+2010}.

@@

@@

@@

\todo{for tom: Refer to appendix figure on formation channel and birth initial mass, mass ratio metallicity (and separation).}

>>>>

@@

A further reason for the preference for low masses is that the population of BHs detectable by LISA primarily come from progenitors that formed from high metallicity gas according to our simulations (see Sec.~\ref{sec:progenitors_and_formation} also Fig.~\ref{fig:progenitor_and_dco_properties}). Stellar winds are stronger at high metallicity leading to increased mass loss. This affects the mass of the most massive black holes that can be formed \citep{Belczynski+2010}.

@@

\todo{@Selma suggests we return to this section. NSs do \textbf{NOT} receive stronger natal kicks in our simulations since most are formed through ECSN e.g. and have 30km/s instead of 265km/s. }

@@

% \newcolumntype{Y}{>{\centering\arraybackslash}X}
% \begin{table}[tb]
%     \centering
%     \begin{tabularx}{\columnwidth}{l|Y Y Y}
%         \hline
%         \multirow{2}{*}{Threshold} & \multicolumn{3}{c}{Individually detectable harmonics} \\ \cline{2-4}
%         & 0 & 1 & 2+ \\
%         \hline
%         $\mathrm{SNR} > 7$ & 18\%  & 67\% & 15\% \\
%         $\mathrm{SNR} > 3$ &  8\%  & 54\% & 38\% \\
%         $\mathrm{SNR} > 1$ &  4\%  & 30\% & 66\% \\
%     \end{tabularx}
%     \caption{Percentage of systems with individual harmonics above different SNR thresholds.}
%     \label{tab:test}
% \end{table}

@@

### 2021-08-19 paper/tex/sections/variations.tex
WR wind text and more

\subsubsection{Stellar wind variation trends}

@@

{\bf Selma would like this one}

>>>>

\subsubsection{Stellar wind variation trends}
We decrease the efficiency of Wolf-Rayet winds to 10\% in model \modWRLow{}. We find that decreasing the efficiency of these winds actually has very little effect on our predicted detection rates. This due to a combination of cancelling effects.

Firstly, the decreased winds mean that the DCOs (particularly those containing BHs) are generally more massive and so more detectable in LISA. Secondly, one may expect that LISA sources in model \modWRLow{} would be higher frequency than in our fiducial model as decreased winds generally result in tighter binaries. However, though this \textit{is} the case at DCO formation, we find by the time the sources have evolved until the LISA mission they are actually at \textit{lower} frequencies than in our fiducial model. This is because the reduced winds allow DCOs to be formed at higher metallicity and, therefore, at more recent times. This means that the DCOs do not evolve for as long before the LISA mission and so remain at lower frequencies (wider separations) thus making them less detectable. Finally, we find that NSNSs are more eccentric and BHBHs are less eccentric than our fiducial model (with BHNSs relatively unchanged). The increase in eccentricity for NSNSs comes from the same reason as the lower frequency, more recent birth times mean that binaries have less time to circularise. The same is not true for BHBHs as the more massive systems are less affected by supernova kicks and so fewer high eccentricity systems are formed.

Overall, despite the large differences in the system properties, these three effects in combination leave the detection rates relatively unchanged.

In model \modWRHigh{} we instead \textit{increase} the efficiency of Wolf-Rayet winds by a factor of 5. In this model the detection rate of BHBHs decreases by over a factor of 10 and BHNSs by over a factor of 2 whilst the NSNS rate is relatively unchanged. Increasing the efficiency of WR winds strongly decreases the final masses of DCOs. This means that many progenitors that would have formed LISA sources under our fiducial assumptions would not have enough mass to produce a DCO, or produce a NS instead of a BH (therefore this effect is stronger on BHBHs than NSNSs). Moreover, DCOs that are formed tend to be less massive and therefore less detectable.

@@

\todo{Selma would like this one}
